---
title: "In-class 4: Correlated Predictors"
author: "[Your name(s) here!]"
date: "31 January 2019"
output: pdf_document
---

## Instructions

1. Rename this document with your student ID (not the 10-digit number, your IU username, e.g. `dajmcdon`). Include your buddy if you are working together.
2. Examine the function below called `generate.data`.
3. Answer the question about the marked line about `X`.
4. Fill in the missing bits in the `intervals` function.
5. In part 3, call the function `intervals` 10 times in a loop. Each time, save the output.
6. Plot the average __width__ of the CI against `cors`.


## Functions to examine and complete

```{r functions-to-create}
# This function generates Y, X1, and X2
## Inputs: n, the number of data points
##         cor, the correlation between X1 and X2
## Outputs: a data frame
generate.data <- function(n, cor){
  epsilon = rnorm(n)
  ## See the question below about X in the following line
  X = matrix(rnorm(2*n),nrow=n) %*% chol(matrix(c(1, cor, cor,1), 2, 2))
  beta = c(3, 2, 1)
  Y = cbind(1, X) %*% beta + epsilon
  df = data.frame(Y, X)
  return(df)
}
## This function finds confidence interval widths 
## for the Linear model
## Inputs: n, the number of data points
##         cor, the correlation between X1 and X2
## Outputs: avg, the average width of the confidence 
##               intervals for the regression
intervals <- function(n, cor){
  df = generate.data(n, cor)
  mdl = lm(Y~X1+X2, data=df)
  itvals =  ## Get the confidences intervals for the bhats (95%)
  widths =  ## Find the width of each interval
  avg = mean(widths[-1]) ## get the average width, ignore intercept
  return(avg)
}
n = 250
cors = seq(.1, 1-1e-5, length.out = 100)
```

## What is the the marked line in `generate.data` doing? Why did I multiply by some matrix?

## Running the simulation and plotting

```{r eval-and-plot}
## preallocate a space to store the interval widths

## write a loop to calculate the average width for each value of cors

## plot cors (x-axis) vs. average widths (y-axis)
##    label your axes nicely
##    make the y-axis on the log scale
```

## How does correlation affect confidence intervals? Try to provide a reason for why this occurs.

edit 2